---
title: "607 week 1 Assignment"
author: "Benson"
date: "2/5/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In the article "Dear Mona Followup: Where Do people Drink the Most Beer, Wine, And Sprits?" by Mona Chalabi, she wants to understand which country drinks most alcohol and what type of alcohol is the favorite. She diverse three kinds of alcohol ( Beer, Spirits, and Wine) to analyze the consumption per serving in each country. 

Article from FiveThirtyEight:
http://fivethirtyeight.com/datalab/dear-mona-followup-where-do-people-drink-the-most-beer-wine-and-spirits/
Dataset:
https://github.com/fivethirtyeight/data/blob/master/alcohol-consumption/drinks.csv



```{r Df}
alcohol_DF <- read.csv(file="https://raw.githubusercontent.com/fivethirtyeight/data/master/alcohol-consumption/drinks.csv",header = TRUE, sep=",") 

summary(alcohol_DF)

#add a new column to category low, moderate, and high consumption alcohol based on the 1st Qu. and 3rd Qu.

library(dplyr)
library(tidyverse)

New_alcohol_DF <- alcohol_DF %>%
  mutate(level_of_comsuption_alcohol = case_when(total_litres_of_pure_alcohol >=7.2 ~ "High",
                                                       total_litres_of_pure_alcohol >= 1.3 ~ "Moderate",
                                                       TRUE ~ "Low")
    
  )

New_alcohol_DF %>%
  slice(1:10)

```
## Data Columns

- country : Country list
- beer_servings : Number of serving in beer
- spirit_servings : Number of serving in spirits
- wine_servings : Number of serving in wine
- total_litres_pf_pure_alcohol : Amount of pure alcohol consumpted 
- level_of_consumption_alcohol : Category the amount of pure alcohol consumpted in Low, Moderate, and High

```{r levelhigh}
high_consumption <- subset(New_alcohol_DF, level_of_comsuption_alcohol == "High")
high_consumption %>%
  select(c(1,5,6))%>%
  arrange(desc(total_litres_of_pure_alcohol))
```

## Conclusions
To extend Mona's analysis, I found that a high consumption alcohol country most likely has its alcohol production. Also, the country's drinking culture is a significant reason for high levels of consuming alcohol while all high levels of consumption alcohol counties had the non-Islamic country. 

extend and verify 
```{r plot}
library(ggplot2)

New_alcohol_DF %>%
  ggplot()+
  geom_bar(aes(y = level_of_comsuption_alcohol, fill =level_of_comsuption_alcohol))+
  ggtitle("Number of countries in different Level of consumption alcohol")+
  xlab("Count")+
  ylab("")+ 
  theme(legend.position = "none")



```

